% CREATED BY DAVID FRISK, 2015
An Informative Headline describing the Content of the Report\\
A Subtitle that can be Very Much Longer if Necessary\\
EMIL ADIELS\\
Department of Some Subject or Technology\\
Chalmers University of Technology \setlength{\parskip}{0.5cm}

\thispagestyle{plain}			% Supress header 
\setlength{\parskip}{0pt plus 1.0pt}
\section*{Abstract}


The brick is an artificial stone invented by humans heating clay into different shapes. With time the use and making of bricks evolved into one of the first modular designs in architecture. The nature of brick and masonry structures is that they only work in compression which makes them very effective but also fragile. The structural efficiency and behaviour has therefore been very dependent of its geometry. For this reason builders,architects and engineers have been using forms which structural action has been through membrane forces, such of shells and vaults.\\

With modern research we can understand and explain the behaviour of these structures. Computational methods has made it possible to generate more complex shapes that satisfies equilibrium. The generation of complex shapes also leaves questions of its geometrical properties,discretization and erection. The mathematical foundation that is used to describe analyse three dimensional surfaces is called \textit{Differential Geometry}. It is a relatively modern field of mathematics that has mostly been used by theoretical physicians explaining the theory of relativity and to some extent by engineers in the \textit{Finite Element Method}.\\

This thesis combines and intersect the fields of traditional craftsmanship, structural masonry, mechanics, geometry and computational methods and how it all comes into the generation of brick shells.The aim is to find a method of how to generate the basis of brick patterns on shells generated using form finding algorithms and methods.    

% KEYWORDS (MAXIMUM 10 WORDS)
\vfill
Keywords: lorem, ipsum, dolor, sit, amet, consectetur, adipisicing, elit, sed, do.

\newpage				% Create empty back of side
\thispagestyle{empty}
\mbox{}