% CREATED BY DAVID FRISK, 2015

\begin{thebibliography}{69}

\bibitem{Reference} Frisk, D. (2015) A Chalmers University of Technology Master's thesis template for \LaTeX . Unpublished.

\bibitem{ref:Struik} Struik, D.J. (1964) Lectures on classical differential geometry. 2nd edn. United States: Dover Publications.

\bibitem{ref:ShellOpt}Adriaenssens, S., Block, P. and Veenendaal, D. (eds.) (2014) Shell structures for architecture: Form finding and optimization. United Kingdom: Routledge.

\bibitem{ref:ArchGeometry}Pottmann, H., Asperl, A., Hofer, M. and Kilian, A. (2007) Architectural geometry. 1 st edn. Bentley Institute Press.

\bibitem{ref:Pressley} Pressley, A. (2012) Elementary differential geometry. 2nd edn. United States: Springer-Verlag London Limited.

\bibitem{ref:Einstein}Gron, O. and Nass, A. (2011) Einstein’s theory. New York, NY, United States: Springer-Verlag New York.

\bibitem{ref:Ochsendorf}Ochsendorf, J. (2011) Guastavino vaulting: The art of structural tile. United States: Princeton Architectural Press.

\bibitem{ref:Heyman}Heyman, J. (1995) Stone skeleton: Structural engineering of masonry architecture - Jacques Heyman - hardcover. United Kingdom: Cambridge University Press.

\bibitem{ref:Form}Allen, E., Zalewski, W. and Foxe, D.M. (2009) Form and forces: Designing efficient, expressive structures [With access Code]. United Kingdom: Wiley, John and Sons.

\bibitem{ref:ConstructionMaterials}Domone, J. and Ilston, J. (2010) Construction materials. ; their nature and behaviour. 4th edn. New York: Taylor and Francis Group.

\bibitem{BrickHistory}Campbell, J.W.P. and Pryce, W. (2003) Brick: A world history. New York: Thames And Hudson.

\bibitem{ref:Pfeifer}Pfeifer, G. 2001, Masonry construction manual, Birkhäuser, Boston;Berlin;Basel;.

\bibitem{ref:Mitchell}Mitchell, C.F. and Chapman, J. (2009) Brickwork and masonry - A practical text book for students, and those engaged in the design and execution of structures in brick and stone. United Kingdom: Read Books.
\bibitem{ref:mortar}Mortar 2016. Britannica Academic. Retrieved 11 August 2016, from
\bibitem{ref:Heyman2}Heyman, J. (1966) ‘The stone skeleton’, International Journal of Solids and Structures, 2(2), pp. 249–279. doi: 10.1016/0020-7683(66)90018-7.

\bibitem{ref:Block} Block,P. (2009) Thrust Network Analysis: Exploring Three-dimensional Equilibrium. Boston: Massachusetts Institute of Technology 
\bibitem{ref:Williams} Williams C.J.K (1980) Form-finding and cutting patterns for air- supported structures. Symposium on Air-supported structures: The state of art: 1 Institution of Structural Engineers. London,99-120
\bibitem{ref:widespan}Barnes, M. and Dickson, M. (eds.) (2000) Widespan roof structures. United Kingdom: Thomas Telford.

\bibitem{ref:Williams2} Williams, C.J.K. (1987) ‘Use of structural analogy in generation of smooth surfaces for engineering purposes’, Computer-Aided Design, 19(6), pp. 310–322. doi: 10.1016/0010-4485(87)90285-5.

\bibitem{ref:Dynamics}Craig, R.R. and Kurdila, A.J. (2006) Fundamentals of structural dynamics. 2nd edn. United States: Wiley, John And Sons.

\bibitem{ref:Dieste}Anderson, S. (2003) Eladio Dieste: Innovation in structural art. United States: Princeton Architectural Press.
\bibitem{ref:Stoker} Stoker, J.J. 1969, Differential Geometry, Wiley-Interscience, New York.

\bibitem{ref:byggmaterial}Burström, P.G. 2007, Byggnadsmaterial: uppbyggnad, tillverkning och egenskaper, 2. uppl. edn, Studentlitteratur, Lund.

\bibitem{ref:Timoshenko} Timoshenko, S. And Woinowsky-Krieger, S. 1959, Theory of plates and shells, 2.th edn, McGraw-Hill, New York.

\bibitem{ref:Wester}Wester, T. (1984) Structural order in space: The plate-lattice dualism. Royal Academy of Arts.
\bibitem{ref:Guastavino} Ochsendorf, J. (2014) Guastavino vaulting: The art of structural tile. United States: Princeton Architectural Press.

\bibitem{ref:GreenZerna}Green, A.E. and Zerna, W. (1992) Theoretical elasticity. 2nd edn. United States: Dover Publications.
\bibitem{ref:Domokos}Domokos, G. 1990, "THE EQUILIBRIUM EQUATIONS OF MEMBRANE SHELLS EXPRESSED IN GENERAL SURFACE COORDINATES", Periodica Polytechnica. Architecture, vol. 34, no. 1-2, pp. 85.

\bibitem{ref:Porter}Porter, D. (1895). Notes on stereotomy. Boston.

\bibitem{ref:lexi} Ahlstrand, J.T., Eriksson, T. And Waldhör, I. 1976, Arkitekturtermer: lexikon över svenska, engelska, tyska och franska arkitektur- och stadsplanetermer : med engelskt, tyskt och franskt register, 2., [revid.] uppl. edn, Studentlitt, Lund.

\bibitem{ref:tegel}Lindgren, J. And Moeschlin, J. 1985, Tegel: tillverkning, konstruktion, gestaltning, Svensk byggtjänst, Stockholm.
\bibitem{ref:murning} Paulsson, G. 1936, Hantverkets bok: 4, Mureri, Lindfors, Stockholm.
\bibitem{ref:maps} Map types (2016) Available at: https://developers.google.com/maps/documentation/javascript
/maptypes (Accessed: 4 August 2016).

\bibitem{ref:MexVault} Coleman Priske (2013) Impressively skilled brick layers, vault contructión. Available at: https://youtu.be/PB8TWMKHHMQ (Accessed: 5 August 2016).
\bibitem{ref:FreiOttoSoap}Frei Otto Film (2015) FREI OTTO - MODELING WITH SOAP FILMS. Available at: https://youtu.be/-IW7o25NmeA (Accessed: 5 August 2016).

\bibitem{ref:brickBrit}Masonry 2016. Britannica Academic. Retrieved 5 August 2016, from http://academic.eb.com.proxy.lib.chalmers.se/levels/collegiate/article/51279
\bibitem{ref:buildConstrBrit}Building construction 2016. Britannica Academic. Retrieved 5 August 2016, from http://academic.eb.com.proxy.lib.chalmers.se/levels/collegiate/article/106103
\bibitem{ref:merc}Mercator projection 2016. Britannica Academic. Retrieved 5 August 2016, from http://academic.eb.com.proxy.lib.chalmers.se/levels/collegiate/article/52078

\bibitem{ref:Pottman}Pottmann, H. 2013, "Architectural Geometry and Fabrication-Aware Design", Nexus Network Journal, vol. 15, no. 2, pp. 195-208.

\bibitem{ref:discrete}Bobenko, A.I., Suris, Y.B. and Bobenko, er I. (2009) Discrete differential geometry: Integrable structure. Washington, DC, United States: American Mathematical Society.


\bibitem{ref:Poulsen}Poulsen, E. (2015) Structural design and analysis of elastically bent gridshells - The development of a numerical simulation tool. Göteborg : Chalmers University of Technology (Diploma work - Department of Applied Mechanics, Chalmers University of Technology, Göteborg, Sweden, nr: 2015:95).



\bibitem{ref:Davis} Davis, L., Rippmann, M., Pawlofsky, T. and Block, P. (2012) ‘Innovative funicular tile vaulting: A prototype vault in Switzerland’, The Structural Engineer, 90(11), pp. 46–56.

\bibitem{ref:Isler}Chilton, J. (2012) ‘Form-finding and fabric forming in the work of Heinz Isler’, .


\bibitem{ref:WorldHistory}Fazio, M.W., Moffett, M. and Wodehouse, L. (2008) A world history of architecture. 2nd edn. London: Laurence King Publishing.
\bibitem{ref:greenVoid}Pohl, E.B. (2008) Green void / LAVA. Available at: http://www.archdaily.com/10233/green-void-lava (Accessed: 5 August 2016).

\bibitem{ref:spef}Sveriges Murnings- och Putsentreprenörsförening (2016) Available at: http://www.spef.org/ (Accessed: 7 August 2016).

Interview

\bibitem{ref:interview} Harvard GSD (2011) ‘Form and forces’ - John Ochsendorf. Available at: https://www.youtube.com/watch?v=r-tG68WvNDM (Accessed: 10 August 2016).

\end{thebibliography}





